Residence time, a master variable of ecology, physiology, and natural selection

### 2015-08-29 analyses/2015_08_29_0720_ResTime.Rmd

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
## Load Data
sim.data <- read.csv("~/GitHub/hydrobide/results/simulated_data/2015_August/25_Aug/SimData.csv")  
#sim.data <- subset(sim.data, motion == ' random_walk ')
```

@@

png(filename = '~/GitHub/hydrobide/results/figs/NandS_vs_ResTime.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "black")

@@

png(filename = '~/GitHub/hydrobide/results/figs/EandB_vs_ResTime.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "black")

@@

png(filename = '~/GitHub/hydrobide/results/figs/Growth_and_Maint.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "black")

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=7}
png(filename = '~/GitHub/hydrobide/results/figs/Diversity_vs_N.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "white")

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
## Loading simulated data csv files

sims <- c()
cts <- c()
tracer.RTDs <- list()
res.RTDs <- list()
ind.RTDs <- list()

inputFile <- "~/GitHub/hydrobide/results/simulated_data/2015_August/25_Aug/IndRTD.csv"
con  <- file(inputFile, open = "r")
ct = 1
while (length(myLine <- scan(con, what="numeric", nlines=1, sep=',', skip=0, quiet=TRUE)) > 0 ){
  line <- as.numeric(myLine)
  cts <- c(cts, line[1])
  sims <- c(sims, line[2])
  rtd <- line[-1:-2]
  ind.RTDs[[ct]] <- rtd
  ct <- ct + 1
  } 
close(con)

inputFile <- "~/GitHub/hydrobide/results/simulated_data/2015_August/25_Aug/TracerRTD.csv"
con  <- file(inputFile, open = "r")
ct = 1
while (length(myLine <- scan(con, what="numeric", nlines=1, sep=',', skip=0, quiet=TRUE)) > 0 ){
  line <- as.numeric(myLine)
  rtd <- line[-1:-2]
  tracer.RTDs[[ct]] <- rtd
  ct <- ct + 1
  } 
close(con)

inputFile <- "~/GitHub/hydrobide/results/simulated_data/2015_August/25_Aug/ResRTD.csv"
con  <- file(inputFile, open = "r")
ct = 1
while (length(myLine <- scan(con, what="numeric", nlines=1, sep=',', skip=0, quiet=TRUE)) > 0 ){
  line <- as.numeric(myLine)
  rtd <- line[-1:-2]
  res.RTDs[[ct]] <- rtd
  ct <- ct + 1
  } 
close(con)
```

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=7}
png(filename = '~/GitHub/hydrobide/results/figs/RTDs.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "white")

t.skews <- c()
i.skews <- c()
r.skews <- c()
t.means <- c()
i.means <- c()
r.means <- c()

colors <- rainbow(length(ind.RTDs))
plot(density(tracer.RTDs[[1]]), col = 'white', xlab='Residence Time',
     xlim = c(0,8), ylim = c(0,2),
     ylab='Probability Density',  main = "Tracer RTD")

ct <- 1
for(rtd in tracer.RTDs){
  if(any(is.na(rtd)) == FALSE){
    lines(density(log(rtd), bw = 0.2), col = colors[ct])
    t.skews <- c(t.skews, skewness(rtd))
    t.means <- c(t.means, mean(rtd))
    }
  ct = ct + 1
}

plot(density(ind.RTDs[[1]]), col = 'white', xlab='Residence time',
  xlim = c(0,8), ylim = c(0,2),
  ylab='Probability Density', main = "Individual RTD")

ct <- 1
for(rtd in ind.RTDs){
  if(any(is.na(rtd)) == FALSE){
    lines(density(log(rtd), bw = 0.2), col = colors[ct])
    i.skews <- c(i.skews, skewness(rtd))
    i.means <- c(i.means, mean(rtd))
    }
  ct = ct + 1
}

#plot(density(res.RTDs[[1]]), col = 'white', xlab='Residence time',
#     xlim = c(0,8), ylim = c(0,2),
#     ylab='Probability Density', main = "Resource RTD")

#ct <- 1
#for(rtd in res.RTDs){
#  if(any(is.na(rtd)) == FALSE){
#    lines(density(log(rtd), bw = 0.2), col = colors[ct])
#    r.skews <- c(r.skews, skewness(rtd))
#    r.means <- c(r.means, mean(rtd))
#    }
#  ct = ct + 1
#}

# Increasing ecosystem residence time shifts the mean of the RTD to higher average values (older individuals). But, it also changes the skewness of the RTD from asymmetrically young to asymmetrically old. No significant effect is seen among tracers.

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=6, fig.height=6}
plot.new()

png(filename = '~/GitHub/hydrobide/results/figs/RTD_shifts.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "white")

par(mfrow=c(1, 1))

plot(log(t.means), t.skews, col = 'grey', xlab='Mean of the RTD, i.e., avg. residence time', ylab='Skewness of the RTD', lwd=2, xlim = c(0,7), ylim = c(-1,2),
     main = "Increasing mean residence time flips the age
     structure of the community from young to old")

points(log(i.means), i.skews, lwd=2, col = 'darkmagenta')
#points(r.means, r.skews, lwd=2, col = 'darkcyan')
lines(c(0,9), c(0,0), lty=2, col='black')

i.OLS <- lm(i.skews ~ log(i.means))
coeff <- summary(i.OLS, correlation = TRUE)
i.slope <- round(coefficients(i.OLS)[2], 3)
i.p <- round(summary(i.OLS)$coefficients[8], 3)
abline(i.OLS, col = "darkmagenta", lw = 2)

t.OLS <- lm(t.skews ~ log(t.means))
coeff <- summary(t.OLS, correlation = TRUE)
t.slope <- round(coefficients(t.OLS)[2], 2)
t.p <- round(summary(t.OLS)$coefficients[8], 2)
abline(t.OLS, col = "grey", lw = 2)

legend("topright", legend = c(paste("Tracers: slope=",t.slope,", p=",t.p), paste("Individuals: slope=",i.slope,", p=",i.p)), pch=19, bty = "n", col = c("grey", "darkmagenta"))

>>>>

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
## Load Data
sim.data <- read.csv("~/GitHub/hydrobide/results/simulated_data/2015_August/29_Aug/SimData.csv")  
#sim.data <- subset(sim.data, motion == ' random_walk ')
```

@@

png(filename = '~/GitHub/hydrobide/results/figs/29_Aug/NandS_vs_ResTime.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "black")

@@

png(filename = '~/GitHub/hydrobide/results/figs/29_Aug/EandB_vs_ResTime.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "black")

@@

png(filename = '~/GitHub/hydrobide/results/figs/29_Aug/Growth_and_Maint.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "black")

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE, fig.width=7, fig.height=7}
png(filename = '~/GitHub/hydrobide/results/figs/29_Aug/Diversity_vs_N.png',
      width = 700, height = 500, units = "px", pointsize = 17, bg = "white")

@@

@@
